### 2016-09-27 TheoremGBF_correctness.tex
minor update GBF proof

The RHS of above expression contains 2 components, $\Prob{\epsilon_{\fn}}$(false-negative probability) and $\Prob{\epsilon_{\fp}}$(false-positive probability). For large values of $m$ and $n$, $\Prob{\epsilon_{\fn}} \approx 0$. On the other hand, $A$ finds one false-positive with $\Prob{\epsilon_{\fp}} \approx 1$ by making $\dbinom{m}{k} - n$ queries at maximum.

@@

Let $\epsilon_{\fp}$ be the event that $A$ finds one false-positive. 
 $$\Prob{\epsilon_{\fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
 The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$. It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions; n is the set of hash indices corresponding to the elements of set, S. Putting together, $\Prob{\epsilon_{\fp}} =  \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)$.

>>>>

The RHS of above expression contains 2 components, $\Prob{\epsilon_{\fn}}= \left(1 - e^{-n/m^k}\right)^{nr}$ (false-negative probability), and $\Prob{\epsilon_{\fp}}=\dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)$ (false-positive probability). For large values of $m$ and $n$, $\Prob{\epsilon_{\fn}} \approx 0$. On the other hand, $A$ finds one false-positive with $\Prob{\epsilon_{\fp}} \approx 1$ by making $\dbinom{m}{k} - n$ queries at maximum.

@@

Let $\epsilon_{\fp}$ be the event that $A$ finds one false-positive. 
 $$\Prob{\epsilon_{\fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
 The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \mathrm{Pr}[h_{1}(x)=i_1$ $\wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k] = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$. It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions; n is the set of hash indices corresponding to the elements of set, S. Putting together, $\Prob{\epsilon_{\fp}} =  \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)$.
